---
title: "Data Cleaning"
output: html_notebook
---
Setting path
NOTE: In order to run the script smoothly we recommend to have saved the folder
containing all the data sets in a separate folder called "Data-OW"
```{r}
path = "../Data-OW/"
```

Importing libraries
```{r}
pacman::p_load(readxl, lubridate, dplyr, timechange)
```

___________________________________________________
# DimProduct dataset

Setting the working directory and importing the datasets
```{r}
head(product.df <- read.csv(paste0(path,"Hackathon_DimProduct_SAN_vShared.csv"), 
                       header = TRUE), 10)
str(product.df)
```

Cleaning ProductKey Column
Note: (i?) is used to render the match case insensitive
```{r}
product.df$ProductKey <- gsub("(i?)key_", "", product.df$ProductKey)
length(product.df$ProductKey)

# OK
```

Cleaning Product Sub-Category column. Indeed, lv2. has some categories that needs to  
be transformed from lower case to upper case before the substitution
```{r}
product.df$ProductCategory_Lvl1 <- toupper(gsub("(\\w*\\s+)", "", 
                                        product.df$ProductCategory_Lvl1))

product.df$ProductCategory_Lvl2 <- toupper(gsub("(\\w*\\s+)", "", 
                                        product.df$ProductCategory_Lvl2))

```

Transforming categories into factors
```{r}
product.df$ProductCategory_Lvl1 <- as.factor(product.df$ProductCategory_Lvl1)
product.df$ProductCategory_Lvl2 <- as.factor(product.df$ProductCategory_Lvl2)
```

____________________
Quick exploration of categories
```{r}
table(product.df$ProductCategory_Lvl1) # Only Category A
```

At lv.1 only A category is present in the dataset

```{r}
table(product.df$ProductCategory_Lvl2)
```
Product suppliers
```{r}
length(unique(product.df$SupplierKey))
```
There are 17 Product suppliers

________________________________________________________________________________
# CPI dataset

```{r} 
head(cpi.df <- read_xlsx(paste0(path, "Consumer Price Index_vShared.xlsx")))
```
Understanding type of variables
```{r}
str(cpi.df)
```

Date columns are already in POSIXct format, no need for change

```{r}
summary(cpi.df)
```
Most of monthly data are missing, thus the information must be reconstructed starting from the daily data. We have noticed that the monthly CPI index is constructed 
by simply taking the first-of-the-month index. Is it correct though? 

Idea: creating the correspondence between month and year, and computing the monthly CPI as the mean of the daily CPI

```{r}
# Creating Date_Monthly and CPI_monthly columns
head(cpi.df1 <- cpi.df %>% 
     group_by(month(Date_daily), year(Date_daily)) %>% 
     mutate(Date_monthly1 = paste0(year(Date_daily),"-",month(Date_daily),"-01"),
             CPI_monthly1 = mean(CPI_daily)))

cpi.df1 <- cpi.df1 %>% 
  ungroup() %>% 
  select(Date_monthly1, CPI_monthly1, Date_daily, CPI_daily)

# Creating the date format for Date_monthly1
cpi.df1$Date_monthly1 <- as.POSIXct(cpi.df1$Date_monthly1)

# Correcting columns name
colnames(cpi.df1) <- c("Date_monthly",
                       "CPI_monthly",
                       "Date_daily",
                       "CPI_daily")
```

Clearing the environment and final check
```{r}
cpi.df <- cpi.df1
remove(cpi.df1)
# Final check
str(cpi.df)

# OK
```

IMPORTANT NOTE:
There is a slight difference in monthly CPI computed as the mean of daily values and the one provided by the data due to the reason stated above. 

___________________________________________________
# Promotion dataset

```{r}
head(promotion.df <- read.table(paste0(path,"Hackathon_DimPromotion_SAN_vShared.csv"), 
                                header = TRUE,
                                sep = ","))
str(promotion.df)
```

Transforming PromotionKey into character (might be transformed into factor later)
```{r}
promotion.df$PromotionKey <- as.character(promotion.df$PromotionKey)
```

Transforming Promotion Dates into POSIXct formats
```{r}
promotion.df$PromotionStartDate <- as.POSIXct(promotion.df$PromotionStartDate,
                                              format = "%m/%d/%Y")

promotion.df$PromotionEndDate <- as.POSIXct(promotion.df$PromotionEndDate,
                                            format = "%m/%d/%Y")
```

Transforming promotion mechanics into factor
```{r}
promotion.df$PromoMechanic <- as.factor(promotion.df$PromoMechanic)
table(promotion.df$PromoMechanic)
```
There are 15 promotion types + 1 unknown

```{r}
summary(promotion.df)
```
No missing values

OK

____________________________________________-
# Store Dataset

```{r}
head(store.df <- read.table(paste0(path, 
                                   "Hackathon_DimStore_SAN_vShared.csv"), 
                           header = TRUE,
                           sep = ","))
```

```{r}
str(store.df)
```

Transforming StoreKey and DistributionChannel into factors
```{r}
store.df$StoreKey <- as.factor(store.df$StoreKey)
store.df$DistributionChannel <- as.factor(store.df$DistributionChannel)
```


Adjusting StoreType and transforming it into factor
```{r}
store.df$StoreType <- gsub("Store Type ", "", store.df$StoreType)
store.df$StoreType <- as.factor(store.df$StoreType)
```

Adjusting Region_lvl 1 and 2 and transforming into factors
```{r}
store.df$Region_Lvl1 <- gsub("Region", "", store.df$Region_Lvl1)
store.df$Region_Lvl2 <- gsub("Region ", "", store.df$Region_Lvl2)

store.df$Region_Lvl1 <- as.factor(store.df$Region_Lvl1)
store.df$Region_Lvl2 <- as.factor(store.df$Region_Lvl2)
```

Final check
```{r}
table(store.df$Region_Lvl1)
as.data.frame(table(store.df$Region_Lvl2))

```

OK

_____________________________________
# Trasaction Dataset

```{r}
setwd(path)
head(transaction.df <- read.table(paste0(path,
                       "Hackathon_FactSalesTransactionDATES_vShared.csv"),
                                  header = TRUE,
                                  sep = ","))
```


Check what 23978 missing values are treated as characters
```{r}
test1 <- transaction.df$TransactionDate
test2 <- transaction.df$TransactionDate

test1 <- as.POSIXct(test1,
                    format = "%Y-%m-%d",
                    tz = "")

verifica <- test2[which(is.na(test1))]

head(verifica)
```

Testing if the same problem is replicated also for other character variables different from date
```{r}
names(transaction.df)
length(which(transaction.df$DayOfWeek == ""))
length(which(transaction.df$WeekendFlag == ""))
```

A recurrent pattern of "" for 23978 observation is present
-> Deleting those observations from the dataset

```{r}
transaction.df <- transaction.df %>% 
  filter(TransactionDate != "")
```

OK

Checking again the summary
```{r}
summary(transaction.df)
```
There are still 72125 missing values in ActualSales

```{r}
str(transaction.df)
```

Trasforming TransactionDate into POSIXct format (it takes a while)
```{r}
head(transaction.df$TransactionDate <- as.POSIXct(transaction.df$TransactionDate, 
                                              format = "%Y-%m-%d",
                                              tz = time_at_tz(
                                              Sys.timezone(location = TRUE))))

```

Transforming DayOfWeek, WeekendFlag, StoreKey and ProductKey into factors
```{r}
transaction.df$DayOfWeek <- as.factor(transaction.df$DayOfWeek)
transaction.df$WeekendFlag <- as.factor(transaction.df$WeekendFlag)
transaction.df$StoreKey <- as.factor(transaction.df$StoreKey)
transaction.df$ProductKey <- as.factor(transaction.df$ProductKey)
```

```{r}
summary(transaction.df)
```
23978 missing transactions: Imputing or removing?

________________________________________________________________________________
# Trasaction Promotion Dataset

```{r}
head(transaction.promotion.df <-read.table(paste0(path,
                                             "Hackathon_FactSalesTransactionPromotion_vShared.csv"),
                                       header = TRUE,
                                       sep = ","))
```

Transforming TransactionDate into POSIXct format
```{r}
transaction.promotion.df$TransactionDate <- as.POSIXct(transaction.promotion.df$TransactionDate,
                                                       format = "%Y-%m-%d")

```

Transforming StoreKey, ProductKey and Promotion Key into factors
```{r}
transaction.promotion.df$StoreKey <- as.factor(transaction.promotion.df$StoreKey)
transaction.promotion.df$ProductKey <- as.factor(transaction.promotion.df$ProductKey)
transaction.promotion.df$PromotionKey <- as.factor(transaction.promotion.df$PromotionKey)
```

```{r}
summary(transaction.promotion.df)
```
OK
_____________________________________
# Holiday

```{r}
head(holiday.df <- read.table(paste0(path,"Hackathon_HolidaysMY_vShared.csv"), 
                                       header = TRUE,
                                       sep = ","))
```

Some information about holidays, we should search each period and merge the information


Merging data sets....
Note: Due to the immense data frame size, we are forced to work piecewise, otherwise
our machines will not able to function well. 
We will subset the data frames in years in order to keep them more manageable
Note: Since the transactions go from 2020.01.01 to 2022.12.31, it has been 
decided to remove the dates that were present concerning dates not in the 
scrutinized timespan

```{r}
cpi.df.period <- cpi.df[between(cpi.df$Date_daily, as.POSIXct("2020-01-01"), as.POSIXct("2022-12-31")),]

promotion.df.period <- promotion.df[between(promotion.df$PromotionStartDate, as.POSIXct("2020-01-01"), as.POSIXct("2022-12-31")),]

```
Now we will split the data frames into 2020, 2021, and 2022
```{r}
# Creating a function "splitting_years" since it will be used more times called

splitting_years <- function(x,start,end){
    for (i in length(colnames(x))){
      if (is.Date(x[,i]) == TRUE){
        df <- x[between(x[,i], 
                     as.POSIXct(start), 
                     as.POSIXct(end)),]
        
    }
    }
  return(df)
}


# For Consumer Price Index
cpi2020 <- splitting_years(cpi.df.period, "2020-01-01", "2020-12-31")
cpi2021 <- splitting_years(cpi.df.period, "2021-01-01", "2021-12-31")
cpi2022 <- splitting_years(cpi.df.period, "2022-01-01", "2022-12-31")

# For promotions
promotion2020 <- splitting_years(promotion.df.period, "2020-01-01", "2020-12-31")
promotion2021 <- splitting_years(promotion.df.period, "2021-01-01", "2021-12-31")
promotion2022 <- splitting_years(promotion.df.period, "2022-01-01", "2022-12-31")

# For transactions
transactions2020 <- splitting_years(transaction.df, "2020-01-01", "2020-12-31")
transactions2021 <- splitting_years(transaction.df, "2021-01-01", "2021-12-31")
transactions2022 <- splitting_years(transaction.df, "2022-01-01", "2022-12-31")

```

Creating the 3 full data sets
Let's start from 2020
```{r}
a <- merge(transactions2020, product.df, by = "ProductKey") 
b <- merge(a, store.df, by = "StoreKey")
c <- merge(b, transaction.promotion.df)
d <- merge(c, promotion2020, by = "PromotionKey")

# Changing the name of Date_daily to perform merge
colnames(cpi2020)[3] <- "TransactionDate"
final2020 <- merge(d, cpi2020, by = "TransactionDate")

```
