---
title: "EDA"
output: html_notebook
---

```{r}
pacman::p_load(ggplot2, tidyverse, lubridate, packcircles, viridis, ggiraph,
               lattice, gcookbook)
```


```{r}
load(file = "transactions2020.RData")
load(file = "transactions2021.RData")
load(file = "transactions2022.RData")
```

```{r}
df <- rbind(transactions2020, transactions2021, transactions2022)
```


# Checking summaries
```{r}
summary(transactions2020)
summary(transactions2021)
summary(transactions2022)
```



# Exploring variables

## Days of the week

```{r}
table(transactions2020$DayOfWeek)
```

Drop unused levels
```{r}
transactions2020$DayOfWeek <- droplevels(transactions2020$DayOfWeek)
```

Reordering levels
```{r}
transactions2020$DayOfWeek <- factor(transactions2020$DayOfWeek,
                                     levels=c('Monday', 'Tuesday', 'Wednesday',
                                              'Thursday', 'Friday', 'Saturday',
                                              'Sunday'))

table(transactions2020$DayOfWeek)
```

```{r}
table(transactions2021$DayOfWeek)
transactions2021$DayOfWeek <- droplevels(transactions2021$DayOfWeek)
transactions2021$DayOfWeek <- factor(transactions2021$DayOfWeek,
                                     levels=c('Monday', 'Tuesday', 'Wednesday',
                                              'Thursday', 'Friday', 'Saturday',
                                              'Sunday'))

table(transactions2021$DayOfWeek)
```

```{r Reordering levels DayOfWeek}
table(transactions2022$DayOfWeek)
transactions2022$DayOfWeek <- droplevels(transactions2022$DayOfWeek)
transactions2022$DayOfWeek <- factor(transactions2022$DayOfWeek,
                                     levels=c('Monday', 'Tuesday', 'Wednesday',
                                              'Thursday', 'Friday', 'Saturday',
                                              'Sunday'))

table(transactions2022$DayOfWeek)

# OK
```


## Weekend Flag
```{r WeekendFlag}
table(transactions2020$WeekendFlag) # Unused levels
transactions2020$WeekendFlag <- droplevels(transactions2020$WeekendFlag)
transactions2021$WeekendFlag <- droplevels(transactions2021$WeekendFlag)
transactions2022$WeekendFlag <- droplevels(transactions2022$WeekendFlag)

table(transactions2020$WeekendFlag)
table(transactions2021$WeekendFlag)
table(transactions2022$WeekendFlag)
```

# Stores overview
```{r Preparing dataset}
# Select the year
yr <- "2020"

store.summary <- rbind(transactions2020, transactions2021, transactions2022) %>% 
  select(StoreKey, StoreType, Region_Lvl1, Region_Lvl2, ActualSales, TransactionDate) %>% 
  filter(year(TransactionDate) == yr) %>% 
  group_by(StoreKey, StoreType, Region_Lvl1, Region_Lvl2) %>% 
  summarise(revenues = sum(ActualSales)) %>% 
  mutate(txt = paste("Store: ",StoreKey, "\n",
                     "Yearly sales: ", round(revenues/1000, digits = 0),"k€", "\n",
                     "Region lvl.1: ", Region_Lvl1, "\n",
                     "Region lvl.2: ", Region_Lvl2)) %>% 
  arrange(desc(revenues)) %>% 
  ungroup()

# Preparing variables
store.summary$StoreKey <- as.character(store.summary$StoreKey)
```

```{r Packed Bubble Chart}
# Generating Layout
packing <- circleProgressiveLayout(store.summary$revenues, sizetype = "area")
data <- cbind(store.summary, packing)
data.gg <- circleLayoutVertices(packing, npoints = 50)

# Plot
p <- ggplot() +
  geom_polygon_interactive(data = data.gg,
                           aes(x = x, y = y, group = id, fill = id,
                               tooltip = data$txt[id], data_id = id),
                           colour = "black", alpha = 0.6) +
  scale_fill_viridis() +
  geom_text(data = data,
            aes(x = x, y = y, label = StoreKey),
            size = 2, colour = "black") +
  theme_void() + 
  theme(legend.position = "none") +
  coord_equal()

# Interactive
widg <- ggiraph(ggobj = p, width_svg = 7, height_svg = 7)
widg
```

How many stores opened or closed from 2020?
```{r Stores opened/closed}
stores.2020 <- unique(transactions2020$StoreKey)
stores.2022 <- unique(transactions2022$StoreKey)

# Stores closed
stores.2020[!(stores.2020 %in% stores.2022)]
print(paste(length(stores.2020[!(stores.2020 %in% stores.2022)]), "stores closed from 2020",
            sep = " "))
# Stores opened
stores.2022[!(stores.2022 %in% stores.2020)]
print(paste(length(stores.2022[!(stores.2022 %in% stores.2020)]), "stores opened from 2020"))

remove(stores.2020, stores.2022)
```

# ProductCategory
```{r Exploring tables}
table(transactions2020$ProductCategory_Lvl2)
table(transactions2022$ProductCategory_Lvl2)
```

# Product Category

```{r Preparing data}
# Select product category
prod.cat <- c("AA", "AB", "AC", "AD", "AE")

transactions.sag <- rbind(transactions2020, transactions2021, transactions2022) %>% 
  select(TransactionDate, ActualSales, ProductCategory_Lvl2) %>% 
  filter(ProductCategory_Lvl2 %in% prod.cat) %>% 
  group_by(ProductCategory_Lvl2) %>% 
  arrange(TransactionDate) %>% 
  mutate(cum_rev = cumsum(ActualSales))

```

```{r Preparing the dataset}
ggplot(data = transactions.sag, aes(x = TransactionDate, y = cum_rev,
                                    fill = ProductCategory_Lvl2)) +
  labs(fill = "Product Category\nLvl. 2", 
       x = "Transaction Date",y = "Cumulative revenues" ) +
  geom_area(color = "black", linewidth = 0.2, alpha = 0.6)
```

AD products are irrelevant when compared to other categories, AE shows a really slow growth, while AA, AB, AC are the best categories in terms of volumes and growth.

# Distribution channels

```{r Preparing the dataset}
# Select distribution channel
dist.channel <- c("Physical", "Online")

dist.channel.sag <- rbind(transactions2020, transactions2021, transactions2022) %>% 
  select(TransactionDate, ActualSales, DistributionChannel) %>% 
  filter(DistributionChannel %in% dist.channel) %>% 
  group_by(DistributionChannel) %>% 
  arrange(TransactionDate) %>% 
  mutate(cum_rev = cumsum(ActualSales))

```

```{r Preparing the dataset}
ggplot(data = dist.channel.sag, aes(x = TransactionDate, y = cum_rev,
                                    fill = DistributionChannel)) +
  labs(fill = "Product Category\nLvl. 2", 
       x = "Transaction Date",y = "Cumulative revenues" ) +
  geom_area(color = "black", linewidth = 0.2, alpha = 0.6)
```

Online distribution channel is a very narrow revenues source with low growth


# Regional distribution

```{r Preparing the dataset}
# Select regions to exclude
regions.exclude.Lvl1 <- c("") # Lvl 1 regions to exclude
regions.exclude.Lvl2 <- c("") # Lvl 2 regions to exclude

reg.distribution.sag <- rbind(transactions2020, transactions2021, transactions2022) %>% 
  select(TransactionDate, ActualSales, Region_Lvl2, Region_Lvl1) %>% 
  filter(!(Region_Lvl1 %in% regions.exclude.Lvl1) | 
           !(Region_Lvl2 %in% regions.exclude.Lvl2)) %>% 
  group_by(Region_Lvl2, Region_Lvl1) %>% 
  arrange(TransactionDate) %>% 
  mutate(cum_rev = cumsum(ActualSales))
```






